### 2014-04-25 ApTranscriptome_TR.Rmd
Minor updates to TR and manuscript

# Load Bioconductor libraries
#source("http://bioconductor.org/biocLite.R")
#biocLite("topGO")
#biocLite("Rgraphviz")
library(topGO) 
suppressMessages(library(Rgraphviz))

@@

```{r gsea_table, echo=FALSE, eval=TRUE, results='asis'}
A22.high.gsea$Type <- "High"
A22.low.gsea$Type <- "Low"
A22.int.gsea$Type <- "Intermediate"
A22.bim.gsea$Type <- "Bimodal"
A22.gsea <- rbind(A22.high.gsea, A22.low.gsea, A22.int.gsea, A22.bim.gsea)
A22.gsea$Colony <- "ApVT"

@@

@@

```{r plot_GOstress, echo=FALSE, eval=FALSE, cache=TRUE}
low.stress.terms <- GO0006950.responsive[intersect(with(GO0006950.responsive, grep("Low", Ar.type)), with(GO0006950.responsive, grep("Low", A22.type))), ]

>>>>

# Load Bioconductor libraries
#source("http://bioconductor.org/biocLite.R")
#biocLite("topGO")
#biocLite("Rgraphviz")
library(topGO) 
#suppressMessages(library(Rgraphviz))

@@

```{r gsea_table_2, echo=FALSE, eval=TRUE, results='asis'}
A22.high.gsea$Type <- "High"
A22.low.gsea$Type <- "Low"
A22.int.gsea$Type <- "Intermediate"
A22.bim.gsea$Type <- "Bimodal"
A22.gsea <- rbind(A22.high.gsea, A22.low.gsea, A22.int.gsea, A22.bim.gsea)
A22.gsea$Colony <- "ApVT"

@@

# in low category
low.genes <- GO0006950.responsive[union(with(GO0006950.responsive, grep("Low", Ar.type)), with(GO0006950.responsive, grep("Low", A22.type))), ]
# in bimodal category
bim.genes <- GO0006950.responsive[union(with(GO0006950.responsive, grep("Bimodal", Ar.type)), with(GO0006950.responsive, grep("Bimodal", A22.type))), ]
# in intermediate category
int.genes <- GO0006950.responsive[union(with(GO0006950.responsive, grep("Intermediate", Ar.type)), with(GO0006950.responsive, grep("Intermediate", A22.type))), ]

@@

```{r plot_GOstress_low, echo=FALSE, eval=FALSE, cache=TRUE}
low.stress.terms <- GO0006950.responsive[intersect(with(GO0006950.responsive, grep("Low", Ar.type)), with(GO0006950.responsive, grep("Low", A22.type))), ]

### 2014-04-25 doc/ApTranscriptome_manuscript.Rmd
Minor updates to TR and manuscript

```{r expression_type_table, echo=FALSE, results='asis'}
pandoc.table(Ap.type.table, style="rmarkdown", caption = "Number of transcripts with maximum expression at high, low, intermediate, both high and low (bimodal) temperatures or are not thermally-responsivefor each species and their overlap.")
```

>>>>

```{r expression_type_table, echo=FALSE, results='asis'}
library(vcd)

pandoc.table(tt2, style="rmarkdown", caption = "Number of transcripts with maximum expression at high, low, intermediate, both high and low (bimodal) temperatures or are not thermally-responsivefor each species and their overlap.")

mosaicplot(tt2, shade = TRUE, xlab = "ApVT", ylab = "AcNC", main = "Mosaic plot of responsive transcripts. For reference, the *High* - *High* cell contains 309 transcripts, while the *Low* - *Low* cell contains 2,417 transcripts")
```
